Experience-Biased Symbolic Planning

### 2014-05-13 AAAI_AuthorKit/paper.tex
bib update

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar \and Mike Phillips \and Maxim Likhachev\\
Carnegie Mellon University\\
5000 Forbes Ave,\\
Pittsburgh, PA 15213\\
\And Sven Koenig\\
University of Southern California\\
Los Angeles, CA 90089
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP STRIPS planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate
experimentally that our planner speeds up HSP by a factor of 2 or more on
many domains while achieving about the same plan quality.
\end{quote}
\end{abstract}

@@

The graph is exponentially larger than its encoding so, in both cases, states are generated only as needed.
The compressed representation sometimes encodes exploitable structure.
In order to create a domain-independent solver for a language such as STRIPS, we need to automatically extract and interpret structural information about the problem.

@@

Since A* expands in a fairly conservative fashion from the start state onward, the start-to-frontier estimates are computed quite accurately by construction of a valid path.
Thus, the principal issue is the derivation of frontier-to-goal estimates.
Given exact distances, it would be a simple matter to trace a valid path from the start, successively taking optimal successors until a goal is reached.
In practice, we are forced to use estimates, which sometimes mislead us into local optima, wasting time on dead-end nodes.

@@

In practice, even using state-of-the-art methods to generate heuristics on isolated planning instances, STRIPS problems can be very difficult to solve without domain knowledge.
Even humans have difficulty when faced with an unfamiliar kind of puzzle, though we get better with experience.
Thus, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.
A recent approach builds \textbf{experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
The intuition is to remember previously generated paths so that, when a new start and goal is queried, a new path can be quickly generated by reusing subpaths from the E-graph.
However, E-graphs have never before been applied to high-level representations such as STRIPS. This is our present contribution.

In section [???], we present the HSP heuristic for STRIPS.
Then, we discuss E-graphs in more technical detail.
This paper's novel contributions follow thereafter, where we extend E-graphs to STRIPS planning by using it to augment the HSP heuristic. 
The resulting weighted A* search is complete and has a configurable suboptimality guarantee.
Finally, we present experiment results in which this use of E-graphs is demonstrated to achieve considerable speedups over experience-free HSP in several planning domains.

@@

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar \and Mike Phillips \and Maxim Likhachev\\
Carnegie Mellon University\\
5000 Forbes Ave,\\
Pittsburgh, PA 15213\\
\And Sven Koenig\\
University of Southern California\\
Los Angeles, CA 90089
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP2 planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate
experimentally that our planner speeds up HSP2 by a factor of 2 or more on
many domains while achieving about the same plan quality.
\end{quote}
\end{abstract}

@@

The graph is exponentially larger than its encoding so, in both cases, states are generated only as needed.
The symbolic representation sometimes encodes exploitable structure.
In order to create a domain-independent solver for a language such as STRIPS, we need to automatically extract and interpret structural information about the problem.

@@

Since A* expands in a fairly conservative fashion from the start state onward, the start-to-frontier estimates are very well-approximated by construction of a valid path.
Thus, the principal issue is the derivation of frontier-to-goal estimates.
Given exact distances, it would be a simple matter to trace a valid path from the start, taking optimal successors at each step, until a goal is reached.
In practice, we are forced to use estimates, which sometimes mislead us into local optima, wasting time on dead-end nodes.

@@

In practice, even using state-of-the-art methods to generate heuristics on isolated planning instances, STRIPS problems can be very difficult to solve without expert domain knowledge.
Even humans have difficulty when faced with an unfamiliar kind of puzzle, though we get better with experience.
Thus, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.

A recent approach builds \textbf{experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
The intuition is to remember previously generated paths so that, when a new start and goals are queried, a new path can be quickly generated by reusing subpaths from the E-graph.
A variant of weighted A* is employed which biases its focus toward the E-graph.
While this work demonstrates promising results in robot motion planning, E-graphs have never before been applied to symbolic domain representations such as the STRIPS language.

Our present contribution is to investigate the use of E-graphs in STRIPS domains. In particular, we take the HSP planner \cite{bonet2001planning} as a representative of the class of modern weighted A* based symbolic planners, and augment its heuristic with a bias toward its E-graph. After presenting the related works, we begin by describing the STRIPS language and the original HSP heuristic. In the following section, we formally introduce E-graphs in technical detail. Then we combine the two approaches, resulting in the new Experience-Biased HSP planner. We present the algorithm and discuss its theoretical properties. This is followed by experiments showing promise for the application of E-graphs to symbolic problem solving. Finally, we conclude with some thoughts on extensions worth investigating.

@@

In recent times, a lot of symbolic planners have emerged based on forward weighted A* search. This paper focuses on augmenting HSP2 as a representative example, because it is fairly simple and forms the foundation of many modern planners. The use of E-graphs is orthogonal to most recent improvements, so our methods can in principle be adapted to any heuristic A* planner.

After HSP2, fast downward and LAMA...
